Introduction

### 2025-02-11 intro.qmd
Remove unnecessary anticipation
...of the term "research compendium"

In the following, we will set the stage by
highlighting the importance of sharing all materials,
documenting their usage,
and linking results with their computations,
leading to the creation _research compendia_.

>>>>

In the following, we will set the stage by
highlighting the importance of sharing all materials,
documenting their usage,
and linking results with their computations.
